---
title: "p8105_hw1_eb3516"
author: "Liz Bekerman"
date: 2023-09-23
output: github_document
---

Setup code to load libraries & open dataset.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(moderndive)
```

#Problem 1

This is the code to load early_january_weather dataset and get the details of the dataset.

```{r}
data("early_january_weather")
early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)
```

The dataset early_january_weather has variables origin, year, month, day, hour, temp, dewp, humid, win_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. All the data has origin EWR and measures hourly weather factors from January 1 - Jan 15, 2013.

According to nrow there are 358 rows and according to ncol there are 15 columns.

```{r}
mean(early_january_weather$temp)
```

The mean temperature is 39.6 degrees.

#Problem 1 Plots

This is the code for plotting time_hour by temp, colored by humid, from early_january_weather dataset.

```{r plots, echo=FALSE}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("HW1_Problem1_Graph.pdf")
```

This plot shows that as time_hour increases, temp increases.


#Problem 2

#Create dataframe
```{r}
norm_sample=rnorm(10,0,1)
df=data.frame(norm_spl=norm_sample,
              bool_spl=norm_sample>0,
              char_spl=LETTERS[1:10],
              factor_spl=factor(rep(1:3, length.out=10),
              levels=1:3))
set.seed(1)
```

#Attempt to calculate means of each vector
```{r}
df%>% pull(norm_spl) %>% mean
```

```{r}
df%>% pull(bool_spl) %>% mean
```

```{r}
df%>% pull(char_spl) %>% mean
```

```{r}
df%>% pull(factor_spl) %>% mean
```

Taking the mean from norm_spl and bool_spl works. Taking the mean from char_spl and factor_spl doesn't work because they don't contain numeric variables.

#Attempt to convert vectors to numeric variables for bool_spl, char_spl, and factor_spl
```{r}
as.numeric(df$bool_spl)
```

```{r}
as.numeric(df$char_spl)
```

```{r}
as.numeric(df$factor_spl)
```

Since bool_spl is a binary true/false, it is translated to binary 0/1.
Char_spl consists of nominal data and therefore as.numeric produces NA values.
Factor_spl is translated into categorical data, labeled 1, 2, and 3.

As.numeric helps explains why the mean is unable to be calculated for char_spl and factor_spl because they are not assigned a numeric value, rather NA (char_spl) or assigned a group (factor).
