---
title: "p8105_hw1_eb3516"
author: "Liz Bekerman"
date: 2023-09-23
output: github_document
---

Setup code to include loading the moderndive library.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(moderndive)
```

#Problem 1

This is the code to load early_january_weather dataset and get the details of the dataset.

```{r}
data("early_january_weather")
early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)
```

The dataset early_january_weather has variables origin, year, month, day, hour, temp, dewp, humid, win_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. All the data has origin EWR and measures hourly weather factors from January 1 - Jan 15, 2013.

According to nrow there are 358 rows and according to ncol there are 15 columns.

```{r}
mean(early_january_weather$temp)
```

The mean temperature is 39.6 degrees.

#Problem 1 Plots

This is the code for plotting time_hour by temp, colored by humid, from early_january_weather dataset.

```{r plots, echo=FALSE}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave("HW1_Problem1_Graph.pdf")
```












